TITLE

### 2021-02-22 outputs/Paper.Rmd
update

---
title: "TITLE"
author: "Adrian Wong, Yingying Zhou, Xinyi Xu, Yang Wu "
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 bookdown::pdf_document2:
 toc: no
subtitle: "SUBTITLE"
abstract: "ABSTRACT"
thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
---

@@

library(tidyverse)
```

>>>>

---
title: "TITLE"
author: "Adrian Wong, Yingying Zhou, Xinyi Xu, Yang Wu "
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 bookdown::pdf_document2:
 toc: no
subtitle: "SUBTITLE"
abstract: "ABSTRACT"
thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
bibliography: references.bib
---

@@

library(tidyverse)
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
